Place of death in NRS COVID-19 deaths: visualisation for 2022 data

### 2022-10-24 covid_nrs_place_of_death_visualisations_2022.Rmd
started working on 'years skipped ahead' plot to illustrate the increase in home deaths

>>>>

# Years 'skipped ahead' due to Covid

There was a pre-pandemic trend of increasing deaths at home - by plotting a regression line we can compute the 'years skipped ahead' equivalent to the increase in deaths at home due to covid

```{r}
regression_data <- 
  merged_proportions_of_deaths_by_place %>% 
  filter(place_of_death == "Home & other non-institution" & year %in% 2015:2019) %>% 
  mutate(years_since_2015 = 0:(n()-1))

regression_model <- lm(data = regression_data, formula = number_of_deaths ~ years_since_2015)

predicted_data <- tibble(years_since_2015 = seq(from=0, to=30, by = 0.1)) %>%
  mutate(year = 2015 + years_since_2015,
         predicted = predict.lm(object = regression_model, newdata = tibble(years_since_2015))
         )

# TODO: make the plot nicer, and print out the predicted year somewhere
# TODO: figure out how to adjust the incomplete 2022 data
actual_data <- tibble(year = c(2020:2022)) %>% 
  left_join(
    merged_proportions_of_deaths_by_place %>%
      select(year, number_of_deaths, place_of_death) %>%
      filter(place_of_death == "Home & other non-institution"),
    by = "year"
  ) %>%
  mutate(
    predicted_year =  if_else(
      condition = year != 2022,
      true = 2015 + (number_of_deaths - coef(regression_model)[1]) / coef(regression_model)[2],
      ## for 2022, we use slightly different computation
      false = NA_real_
    ),
    label = paste0("Actual home deaths in ", year)
  )

ggplot(data = predicted_data, aes(x=year, y=predicted)) + 
  geom_point(data = regression_data, aes(x = year, y = number_of_deaths)) +
  geom_line(linetype = "dashed") +
  ggrepel::geom_label_repel(data = actual_data, aes(x = predicted_year, y = number_of_deaths, label = label)) +
  geom_vline(data = actual_data, aes(xintercept = predicted_year)) +
  xlim(c(2015,2035)) +
  theme_minimal() +
  scale_y_continuous(labels = scales::comma)
```
